Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-23 article.rnw
Remove an unnecessary sentence in the discussion.
Add a missing referenceregarding the multivariate nature of niche.

One possible explanation is that species simply do not group to the same extent in a quantitative competitive context as in a binary network.
That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses \parencite{XXX}.
In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown clearer groupings.
Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.

@@

The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{XXX}.
This could suggest that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.

>>>>

One possible explanation is that species simply do not group to the same extent in a quantitative competitive context as in a binary network.
That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown clearer groupings.
Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.

@@

The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.
This could suggest that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
